Individual Variation in Animal Movement

### 2021-02-14 movement_paper/rudolph_ch2.Rmd
Add citation format

---
title: "Individual Variation in Animal Movement"
abstract: |
  This should be the abstract
output:
  html_document:
    df_print: paged
  word_document: default
bibliography: aracari_movement.bib
---

>>>>

---
title: "Individual Variation in Animal Movement"
abstract: |
  This should be the abstract
output:
  html_document:
    df_print: paged
  word_document: default
bibliography: aracari_movement.bib
csl: ecology-letters.csl
---
